
### {{pair_name}}

```{r message=FALSE, warning=FALSE}

omics = omics_list[[{{i}}]]

if ( omics == "EBD" ){
        phyXpp <- subset_samples(ps.clean.cca, !is.na(claudin2) & !is.na(FABP2))
        Mtb <- sample_data(phyXpp)[,c("claudin2","claudin3","FABP2")] %>% log()
        
} else if (omics == "cytokine"){
        phyXpp <- subset_samples(ps.clean.cca, !is.na(IL_1beta))
        Mtb <- sample_data(phyXpp)[,c(13, 15, 16)] %>% log() 

} else if (omics == "SCFA"){
        phyXpp <- subset_samples(ps.clean.cca, !is.na(valeric_acid) )
        Mtb <- sample_data(phyXpp)[,c(17:24)] %>% log()

}
```


**Regularized CCA using `mixOmics`**

```{r message=FALSE, warning=FALSE}
#devtools::install_github('mortenarendt/StructuralKnowledgeModl')
phyXpp <- filter_taxa(phyXpp, function(x) sum(x>0)>0, TRUE)
phyXpp <- transform_sample_counts(phyXpp, function(x) x/sum(x))
OTUtb <- data.frame(otu_table(phyXpp))
```


```{r message=FALSE, warning=FALSE}
# scale the variables
GM <- as.matrix(scale(OTUtb, center = T)) 
mtb <- as.matrix(scale(Mtb, center = T))
rownames(GM) = rownames(mtb)
```


```{r message=FALSE, warning=FALSE}
set.seed(42)
X <- mtb # extract all lipid concentration variables
Y <- GM # extract all gene expression variables

# Using the Shrinkage (shrinkage) Method
result.rcca.shrinkage <- rcc(X, Y, method = 'shrinkage')
```


Sample plot

```{r message=FALSE, warning=FALSE}
# sample plots
# plot the projection of samples for shrinkage rCCA data
plotIndiv(result.rcca.shrinkage, comp = 1:2,
          ind.names = sample_data(phyXpp)$time,
          group = sample_data(phyXpp)$group, rep.space = "XY-variate",
          legend = TRUE, title = 'rCCA shrinkage XY-space', guide = "none", cex = 6)

```


Arrow plot

```{r message=FALSE, warning=FALSE}
plotArrow(result.rcca.shrinkage, group = sample_data(phyXpp)$group, col.per.group = color.mixo(1:2),
          title = "rCCA shrinkage method")
```


Variable plot

```{r message=FALSE, warning=FALSE}
plotVar(result.rcca.shrinkage, var.names = c(TRUE, TRUE), cex = c(4,4), cutoff = 0.5,
        title = "rCCA shrinkage comp 1-2", style = "ggplot2") 
```


Relevance network plot and clustered image map

A more robust way to evaluate the correlation structure is through a relevance network plot. The circular nodes represent EBD markers and the rectangular nodes represent taxa. The bipartite relationships between these non-negligibly correlated features can be seen by the color of the connecting lines (edges). 


```{r message=FALSE, warning=FALSE, eval=FALSE}
# network
network(result.rcca.shrinkage, comp = 1:2, interactive = FALSE, color.node = c("orange","lightblue"), lwd.edge = 2, cutoff = 0.5, color.edge = rev(color.jet(100)), save = "png", name.save = paste("output/network", omics, sep = "_"))
```


```{r echo=FALSE}
pngconvert( FileName = paste(paste("output/network", omics, sep = "_"), "png", sep = ".") )

knitr::include_graphics(path = paste0(paste("output/network", omics, sep = "_"), ".png"))
```


Above graph shows the correlation structure for all bipartite relationships with a correlation above 0.5. There is a reasonably complex correlation structure; there were two clusters. 

To complement the network plot, a clustered image maps (CIM) can be used (bellow). While CIM plot does not have a cutoff which aids in determining the number of feature clusters, the correlations seen here do reflect that seen in network plot – such that there are roughly three clusters.


```{r message=FALSE, warning=FALSE, eval=FALSE}
# heatmap
cim(result.rcca.shrinkage, comp = 1:2, margins = c(10,12), color = rev(color.jet(25)), save = "png", name.save = paste("output/heatmap", omics, sep = "_"))
```


```{r echo=FALSE}
pngconvert( FileName = paste(paste("output/heatmap", omics, sep = "_"), "png", sep = ".") )
knitr::include_graphics(path = paste0(paste("output/heatmap", omics, sep = "_"), ".png"))
```

